From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2017-02-16 2015CompleteDerivation/pictures/temporalDof.tex
Updating colors for figures

@@

		% drawing the first shape
		\filldraw[black,fill=blue,opacity=0.5] (0,0) -- ($(p2)$) -- ($(p3)$) -- cycle;

		\filldraw[black,fill=blue,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={0:(0,0)}] (0,0) rectangle ($(p7)$) node[pos=.5] {\large $\omega$};

		\draw[black,fill=blue,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={\thetavar:(0,0)}] (0,0) rectangle ($(p8)$) node[pos=.5, rotate=\thetavar] {\large $dq\wedge dp$};

		\draw[black,fill=blue,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={0:(0,0)}] ($(p2)$) rectangle ($(p5)$) node[pos=.5] {\large $dt\wedge dE$};

@@

		%drawing the shape on the right
		\filldraw[black,fill=green,opacity=0.5] ($(h0)$) -- ($(h2)$) -- ($(h3)$) -- cycle;

		\filldraw[black,fill=green,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={0:($(h0)$)}] ($(h0)$) rectangle ($(h7)$) node[pos=.5] {\large $\omega$};

		\draw[black,fill=green,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={\phivar:($(h0)$)}] ($(h0)$) rectangle ($(h8)$) node[pos=.5, rotate=\phivar] {\large $dq\wedge dp$};

		\draw[black,fill=green,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={0:($(h0)$)}] ($(h2)$) rectangle ($(h5)$) node[pos=.5] {\large $dt\wedge dE$};

>>>>

		% styles
		\tikzstyle{triangle}=[ultra thick,fill=white,opacity=0.5];
		\tikzstyle{projection} = [fill=yellow,fill opacity=0.1,text opacity =1,text=black];

@@

		% drawing the first shape
		\filldraw[style=triangle] (0,0) -- ($(p2)$) -- ($(p3)$) -- cycle;

		\filldraw[style=projection,rotate around={0:(0,0)}] (0,0) rectangle ($(p7)$) node[pos=.5] {\large $\omega$};

		\draw[style=projection,rotate around={\thetavar:(0,0)}] (0,0) rectangle ($(p8)$) node[pos=.5, rotate=\thetavar] {\large $dq\wedge dp$};

		\draw[style=projection,rotate around={0:(0,0)}] ($(p2)$) rectangle ($(p5)$) node[pos=.5] {\large $dt\wedge dE$};

@@

		%drawing the shape on the right
		\filldraw[style=triangle] ($(h0)$) -- ($(h2)$) -- ($(h3)$) -- cycle;

		\filldraw[style=projection,rotate around={0:($(h0)$)}] ($(h0)$) rectangle ($(h7)$) node[pos=.5] {\large $\omega$};

		\draw[style=projection,rotate around={\phivar:($(h0)$)}] ($(h0)$) rectangle ($(h8)$) node[pos=.5, rotate=\phivar] {\large $d\hat{q}\wedge d\hat{p}$};

		\draw[style=projection,rotate around={0:($(h0)$)}] ($(h2)$) rectangle ($(h5)$) node[pos=.5] {\large $d\hat{t}\wedge d\hat{E}$};
